Java Based Memory Latency Simulator

### 2020-11-21 finalPaper/paper.tex
Updated final paper and ref

Rotatational latency of a hard drive is how long does it take a platter to spin, as after all it is a mechanical
component bounded by a certain speed.
According to Eric Shanks from ithollow.com, the following were the Hard Drive Rotational latencies in 2013.

@@

Seek time; which is the time it takes for the Read-Write to move up and down the platter.
The Seek time itself is comprised of a series of phase times. The first being the acceleration phase,
the read write arm starts to move, then comes the coasting phase when the arm is moving at full speed. This
is followed by the deceleration phase where the read write arm slows down. Then finally comes the
settling phase as the read write head stops right at the data it needs.
The average seek time of hardrives of size 300 GB to 1TB ranged from an average time of 4ms to 9ms.
(source: pages.cs.wisc.edu - Operating Systems: Three Easy peices peices - Remzi Arpaci, Andrea Arpaci).

The last part of total I/O latency for hard drive is the transfer time, which is the time it takes the
data to be transfer from or to the Read-Write head. Compared to Rotational Latency and seek time, transfer
time is insignificant, given that the mechanical movements take more time than data movement which is more of
movement of energy packets.

@@

As of 2012 these were some of the Latencies, that includes different operation on a low level
and at the high level.(Source: gist/github.com/jboner/2841832)

@@

\singlespace
\bibliographystyle{abbrv}
\bibliography{references}
www.ithollow.com/2013/11/18/disk-latency-concepts/
pages.sc.wisc.edu/~remzi/OSFEP/file-disks.pdf
www.tomshardware.com/reviews/cas-latency-ram-cl-timings-glossary-definition,6011.html
research.ece.cmu.edu/safari/thesis/kchang_dissertation.pdf
people.cs.pitt.edu/~cho/cs1541/current/handouts/lect-memh_4up.pdf

>>>>

Rotatational latency of a hard drive is how long does it take a platter to spin, as after all it is a mechanical
component bounded by a certain speed.
According to \cite(1) Eric Shanks from ithollow.com, the following were the Hard Drive Rotational latencies in 2013.

@@

Seek time; which is the time it takes for the Read-Write to move up and down the platter.
The Seek time itself is comprised of a series of phase times. The first being the acceleration phase,
the read write arm starts to move, then comes the coasting phase when the arm is moving at full speed. This
is followed by the deceleration phase where the read write arm slows down. Then finally comes the
settling phase as the read write head stops right at the data it needs.
The average seek time of hardrives of size 300 GB to 1TB ranged from an average time of 4ms to 9ms.
(source: pages.cs.wisc.edu - Operating Systems: Three Easy peices peices - Remzi Arpaci, Andrea Arpaci).
(source: \cite }
The last part of total I/O latency for hard drive is the transfer time, which is the time it takes the
data to be transfer from or to the Read-Write head. Compared to Rotational Latency and seek time, transfer
time is insignificant, given that the mechanical movements take more time than data movement which is more of
movement of energy packets.

@@

As of 2012 these were some of the Latencies, that includes different operation on a low level
and at the high level.(Source: }

@@

The goal of the project was to find out about the varying latencies of some of the major components of the CPU, with
or without the simulator. By implementing a simulator good enough to differentiate and manage data we were able to
find out more about the

\singlespace
\bibliographystyle{abbrv}
\bibliography{references}
